Carbonate chemistry at Ny-Ålesund

### 2021-03-22 awipev-CO2.Rmd
k1k2 revised figs names
cosmetic changes

ggsave(filename = "figures/lueker-sulpis.png", plot = p, width = 25, height = 20, units = "cm")

@@

```{r save for k1k2 report, echo=FALSE, message= FALSE, warning=FALSE}

>>>>

ggsave(filename = "figures/k1k2_all.png", plot = p, width = 25, height = 20, units = "cm")
ggsave(filename = "figures/k1k2_temperature.png", plot = p3, width = 25, height = 20, units = "cm")

@@

```{r save elements for k1k2 report, echo=FALSE, message= FALSE, warning=FALSE}
